A Domain Specific Language for Functional Code Fusion for Intrusion Detection Algorithms in Wireless Sensor Networks

### 2014-09-22 paper.tex
added initial references

DSL for WSN

DSL for IDS

Code Generation for WSN

Code Optimization for embedded systems/WSN

Code Generation for IDS

@@

Theory of Loop Fusion

Examples of code/loop fusion (e.g. Haskell Stream Fusion)

Function Inlining (e.g. TinyOS)

@@

@@

TODO: memory usage

2 algorithms
TODO: adding 3rd ?

@@

@@

% \bibliographystyle{IEEEtran}
% \bibliography{referenties}

>>>>

DSL for WSN \cite{naumowicz2009prototyping,levis2004tinyscript}

DSL for IDS \cite{eckmann2002statl}

Code Generation for embedded systems/WSNs \cite{leupers2000code,marwedel2002code}

Code Optimization for embedded systems/WSNs \cite{panda2001data,naik2001software}

Code Generation for IDS \cite{charitakis2003code}

@@

Theory of Loop Fusion \cite{darte2000complexity}

Examples of code/loop fusion (e.g. Haskell Stream Fusion) \cite{coutts2007stream}

Function Inlining (e.g. TinyOS) \cite{gay2007software,gay2003nesc}

@@

TODO

\section{Problem Solution}

TODO

@@

TODO: memory usage ?

2 algorithms

TODO: add 3rd ?

@@

explore more domains + implement corresponding DSLs for embedded systems

extract generic language as host for DSLs

@@

\bibliographystyle{IEEEtran}
\bibliography{literature/referenties}
